---
title: "linear model from Web"
author: "Syi-yonnie Richard"
date: "Fall 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot
```{r}
plot(SIMS~ARM,data=data)
```

Based off of the plots image, we can see that the scatter plot has a positive shift since it shifts right.  
### Numerical results
```{r}
cor(SIMS~ARM,data=data)
```

Based off of the number, we can observe that there's a positive correlation.  

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

This model shows a formula line of Residuals and Coefficient arithmetic.
SIMS= 0.054563*ARM-4.095160

#### Predict at target point

SIMS

```{r}
0.054563*88-4.095160
```

While plugging in 88 and removing ARM we got the result number 0.707384 which helps us predict what the number could be.

```{r}
new <- data.frame(ARM = 88, GRIP=94)
```

```{r}
predict(model.1, new, interval = "prediction")
```

This prediction gives us a similar results from the last the last prediction (prediction at target point).

#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point() + geom_smooth(method=lm)
```

This chart gives us the possible scatter plot/line solution for our data. 

## Model 2 SIM~GRIP



### Now add in scatterplot
```{r}
plot(SIMS~GRIP,data=data)
```


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

This SIMS x GRIP result has a smaller number compared to the SIMS x ARM result.
### Inferential  (Build model.2)
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  

This model shows a larger result of numbers in it's residuals area,
which, is opposite from SIMS and ARMS result numbers with, SIMS and ARMS showing result #'s of 0.7 while Residuals max shows a higher result number of 3.3.

#### predict model.2 at target point

```{r}
predict(model.2, new, interval = "prediction")
```
```{r}
0.045463*94-4.809675
```
Our prediction number based off the model plot is -0.5361543.

#### now add the model fit to our plot for model.2
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
basicNN + geom_point() + geom_smooth(method=lm)
basicNN + geom_point(method=lm)
```

This is the GRIP model result. This GRIP plot shows the same result as the ARM plot in the beginning. If we use the prediction value it matches x=94 for GRIP.

## Model 3 SIM~ARM+GRIP



### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

We have a positive correlation between ARM and GRIP so far based on the multiple results we got in numerical results. GRIP shows a higher percentage (0.6398458) than ARM (0.6860073) but both numbers still show a positive correlation since their almost similar.  

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS ~GRIP + ARM,data=data)
summary.lm(model.3)
```

This model shows a higher percentage of numbers than model 2. We can predict that the numbers are gonna be in a higher percentage than 0.

#### predict model.3 at target point
  
```{r}
predict(model.3, new, interval = "prediction")
```  

Our residual standard error 1.144 which is smaller than our other models, and our multiple R-squared is bigger, which makes it better and a more reliable prediction.

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```

Model 1 used the Data of SIMS and ARMS while Model 2 used the data of SIMS ~ GRIP + ARM which shows some comparing and contrasting in data. Both models confide in using the data in SIMS and ARM which shows the slight comparison. Both models compared with using numbers that start with 14 (Model 1 145.217.88 & Model 2 144 188.43.

### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```

Both models use the SIMS and GRIP data which helps them compare in predicting numbers in the same percentage range. Both models have numbers that compare with their numbers starting with 14, Model 1's number is estimated at 145 while Model 2's number starts off with 144, both numbers comparing with the way they start off.

## Informally compare Model.1 with model.2

